Web Service Community \\ Learning

### 2014-07-07 papers/webservice-coalition-learning/webservice_coalition_learning.tex
changes

@@

\subsection{The join challange}\label{s:tjc}

\subsection{Join Consiquences}\label{s:jc}

>>>>

With a group of web services having identical or similar functionalists, quality of service metrics provide nonfunctional characteristics for the optimal candidate selection. Web service quality metrics have been presented in \cite{Ardagna:2007:ASC:1263152.1263531,Menasce:2002:QIW:613357.613758,10.1109/ISSRE.2011.17}, we have adopted the most representative QoS properties of web services which highly influence the utility of web services.

\begin{itemize}

  \item \emph{Throughput} is the rate at which a service can process requests. QoS measures can include the maximum throughput or a function that describes how throughput varies with load intensity.

	\item \emph{Availability} is the percentage of time that a service is operating.
	The probability that the service operation is accessible. Availability is a number in the range [0, 1].

	\item \emph{Response Time} is the time a service takes to respond to various types of requests. Response time is a function of load intensity, which can be measured in terms of arrival rates (such as requests per second) or number of concurrent requests. QoS takes into account not only the average response time, but also the percentile (95th percentile, for example) of the response time.	
	The expected delay between the time instant when a request is sent and the time when the result is obtained. Execution time is measured in seconds.

	\item \emph{Data Quality} The ability of a data collection to meet user requirements , defined as the proximity of a value v returned by wsj;o to a value v0 considered as
correct. The measure of data quality is considered here as a real number in the range [0, 1], where 1 represents the most desirable score.

\end{itemize}

@@

\subsection{The join challenge}\label{s:tjc}

\subsection{Join Consequences}\label{s:jc}

\section{The Model}\label{s:model}
